An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-23 VLDB2026/main.tex

		\multicolumn{2}{|c|}{\textbf{Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
		 \\ \hline
		\multirow{6}{*}{\textbf{AF}} 
		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Flexible Attributes & N   & Y   & Y   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Complex Boolean     & N   & N   & N   & N   & Y   & N   & N   & \multicolumn{5}{c|}{} \\ \hline

@@

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms.}.

@@

	\begin{table}[t]
		\centering

		\caption{Algorithm Recommendation per Scenario}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{|l|c|c|}
				\hline
				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
				\hline
				S1: Large-scale Datasets & Puck, UNG & iRange\\[1pt]
				\hline
				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\[1pt]
				\hline
				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\[1pt]
				\hline
				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\[1pt]

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\[1pt]
				\hline
				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\[1pt]
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\[1pt]
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\[1pt]
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}
	\end{table}

>>>>

		\multicolumn{2}{|c|}{\textbf{Characteristics/Algorithm}} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win}
		 \\ \hline
		\multirow{6}{*}{\textbf{AF}} 
		& Filter Type         & C   & C   & C   & C   & B   & B   & B   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& AND                 & Y   & N   & N   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{\multirow{4}{*}{\centering\shortstack{AF\\not support}}} \\ \cline{2-9}
		& OR                  & N   & Y   & Y   & N   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Flexible Attributes & N   & Y   & Y   & Y   & Y   & Y   & Y   & \multicolumn{5}{c|}{} \\ \cline{2-9}
		& Complex Boolean     & N   & N   & N   & N   & Y   & N   & N   & \multicolumn{5}{c|}{} \\ \hline

@@

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig:Big_Dataset_range}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.

@@

		\caption{\textcolor{orange}{Recommendations}}
		\small

		\label{tab:compair_2}

		\resizebox{\textwidth}{!}{
			\begin{tabular}{|l|*{16}{c|}}
				\hline
				\textbf{Application Scenarios / Algorithm} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{ACORN} & \textbf{UNG} & \textbf{Puck} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
				\hline
				\textbf{Query Performance} & H & M & H &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\textbf{Index Time} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\textbf{High LID Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\textbf{Peak Memory} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\textbf{General-Purpose} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\textbf{Large-Scale Dataset} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\textbf{Rare Attribute \& Low Range} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\textbf{Insensitive to Data Distribution} &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
				\hline
			\end{tabular}
		}
		\centering
	\end{table*}
